\section{A Historical Perspective of Speech Recognition}

• This 2014 paper, authored by Xuedong Huang, James Baker, and Raj Reddy, provides a historical overview of automatic speech recognition (ASR) research, tracing its evolution from the early days of limited capabilities in 1976 to the current era of sophisticated voice assistants like Siri and Google Assistant. The authors highlight the key breakthroughs that have driven ASR's progress, including the development of hidden Markov models (HMMs), statistical modeling techniques, and the advent of deep neural networks (DNNs).

• The paper emphasizes the importance of large datasets and computing power in advancing ASR, noting that Moore's law has played a crucial role in enabling the development of increasingly complex and accurate systems. However, the authors also acknowledge the limitations of current ASR systems, particularly in handling noisy or accented speech, and highlight the need for further research in areas like data efficiency, robustness, and generalization.

• The authors identify six main challenges that must be addressed to move ASR to the next level, including the need for more data, improved computing infrastructure, better handling of uncertainties, and more robust speaker-independent and adaptive systems. They also discuss the importance of incorporating prosody (intonation, rhythm, and stress) into ASR models, as this crucial aspect of human speech has been largely ignored in the past.
--

\section{Trends and Developments in Automatic Speech Recognition Research}

•	This 2023 paper, authored by Douglas O'Shaughnessy, delves into the intricacies of automatic speech recognition (ASR) research, focusing on the unique challenges posed by the complex nature of human speech. The author contrasts the traditional approach of using hidden Markov models (HMMs) with the more recent trend of employing deep neural networks (DNNs), highlighting the advantages and limitations of each approach. The paper emphasizes the importance of understanding the acoustic-phonetic properties of speech, as well as the limitations of current ASR systems in handling noisy or accented speech.

•	O'Shaughnessy explores various aspects of speech analysis, including spectral analysis, Mel-frequency cepstral coefficients (MFCCs), and formant tracking, and discusses the trade-offs between accuracy and computational efficiency. He also examines different types of supervised and unsupervised learning methods used in ASR, along with the challenges of data scarcity and speaker variability.

•	The paper concludes by suggesting potential avenues for future research in ASR, including the development of more robust and efficient systems that can better handle noisy and accented speech, incorporate prosody, and exploit the unique characteristics of human speech. The author emphasizes the need for a deeper understanding of the underlying principles of speech production and perception to guide the development of more effective ASR systems.

